\documentclass[]{article}
% twoside,leqno,twocolumn
\twocolumn

\usepackage{booktabs, braket} % For formal tables
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{graphicx}
\usepackage{blkarray}
\usepackage{comment}
\usepackage[algo2e]{algorithm2e}

\usepackage{ltexpprt} % alenex format

\DeclareMathOperator{\X}{X}
\DeclareMathOperator{\tr}{\text{tr}}		     % trace
\DeclareMathOperator{\Ap}{$A$ ^\prime} 		     % A'
\DeclareMathOperator{\bp}{$b$ ^\prime} 		     % b'
\DeclareMathOperator{\Xb}{\mathcal{X}}		     % big X
\DeclareMathOperator{\A}{\mathcal{A}}
\DeclareMathOperator{\R}{\mathbb{R}}

\begin{document}

\newcommand{\todo}[1]{{\color{red}{[{\bf TODO:} #1]}}}

\title{Optimal Quantum Algorithms via Semidefinite Programming}

% Comment out for submission
\author{Michael Czekanski
\and R. Teal Witter
\thanks{Department of Computer Science and Engineering, NYU Tandon}}

\date{}

\maketitle

% Copyright statement
\fancyfoot[R]{\scriptsize{Copyright \textcopyright\ 2020 by SIAM\\
Unauthorized reproduction of this article is prohibited}}

\graphicspath{{./../figures/}}

\begin{abstract}
 \begin{enumerate}
    \item Optimal quantum query complexity
    \item Worst case inputs
    \item span program to solve
    \item arbitrary precision
    \item comparison to another solver?
    \item problem specific SDP enhancements
\end{enumerate}



Improvements in quantum computing research have led to an
increased focus on the development of quantum algorithms. This
field is of great interest as it has been shown that quantum 
computers are more efficient at solving certain problems than 
their classical counterparts. Thus the identification of such 
problems is an important part of quantum computing research. We 
implement an algorithm that can calculate the optimal quantum 
query complexity for a given Boolean function as well as the 
corresponding quantum algorithm. This tool should allow 
researchers to easily identify Boolean functions for which 
quantum computers would be much more efficient as well as provide the details for implementation. More formally, we solve a 
semidefinite programming problem for a given function $f$ to 
calculate the fewest number of queries of the an input that a 
quantum computer would need to evaluate $f$ and use the results 
of this optimization problem to provide the corresponding span 
program that is optimally solved by a quantum computer.

\begin{comment}
We implement an algorithm that takes in a 
Boolean function and outputs the optimal
quantum query complexity of the function 
as well as a query optimal span program
for evaluating it on a quantum computer. 
Let $f$ be a Boolean function
and $x$ be a bitstring input to $f$.
We consider the query model where
an algorithm evaluates $f(x)$
by asking an oracle about the bits of $x$.
The optimal quantum query complexity of $f$
is the fewest queries any quantum algorithm
takes to determine $f(x)$ over all inputs $x$.
We find the optimal quantum query complexity
of $f$ by solving a semidefinite 
programming (SDP) problem.
The SDP solution also provides a span program 
that evaluates $f$ in optimal
quantum query complexity. Our numerical results prove to be in line with general analytic understanding, and the span programs we implement are shown to correctly evaluate the given function.
\end{comment}
\end{abstract}


\input{sec/intro.tex}
\input{sec/background.tex}
\input{sec/implementation.tex}
\input{sec/results.tex}
\input{sec/discussion.tex}

\bibliographystyle{abbrv}
\bibliography{main}

\end{document}