\documentclass[acmtog]{acmart}
%acmtog if we're feeling a little funky ;)

\usepackage{booktabs, braket} % For formal tables
\usepackage{cleveref}
\usepackage{graphicx}
\usepackage{blkarray}

\settopmatter{printacmref=false} % Removes citation info after abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference informat\textbf{}ion in first column
\usepackage{fancyhdr}

\DeclareMathOperator{\X}{\mathbb{X}}		     % expected value
\DeclareMathOperator{\tr}{\text{tr}}		     % trace
\DeclareMathOperator{\Ap}{$A$ ^\prime} 		     % A'
\DeclareMathOperator{\bp}{$b$ ^\prime} 		     % b'
\DeclareMathOperator{\Xb}{\mathcal{X}}		     % big X
 
\pagestyle{fancy}
\fancyhf{}
\lhead{Czekanski \& Witter, Fall 2019}
\rfoot{\thepage}
\newcommand{\todo}[1]{{\color{red}{[{\bf TODO:} #1]}}}

%\pagestyle{plain} % removes running heades

% Use the "authoryear" citation style, and make sure citations are in [square brackets].
\citestyle{acmauthoryear}
\setcitestyle{square}

% A useful command for controlling the number of authors per row.
% The default value of "authorsperrow" is 2.
\settopmatter{authorsperrow=1}

\begin{document}


% Title. 
% If your title is long, consider \title[short title]{full title} - "short title" will be used for running heads.
\title{Implementing a Semidefinite Program Solver to 
Find the Optimal Quantum Query Complexity
of Boolean Functions}

% please leave the subtitle!
\subtitle{Middlebury College, Fall 2019}

% Authors.
\author{Michael Czekanski}
\affiliation{%
  \institution{Middlebury College}}

\author{R. Teal Witter}
 \affiliation{%
   \institution{Middlebury College}}

\maketitle

\graphicspath{{./../figures/}}
% a couple of paragraphs describing your project
\section*{Abstract}

With the increasing feasibility of large scale quantum computers, the
development of optimal quantum algorithms has become
an important area of research.
Through properties of quantum mechanics, such as
superposition and phases, quantum computers can
accomplish certain tasks more efficiently than
classical computers. These properties essentially
allow us to put multiple inputs into a single function
at once. Therefore the number of times quantum
computers must query an input can be drastically
lower than the number of times a classical computer
would need. The number of queries of an input is
naturally thought to well approximate the runtime of
an algorithm. Existing research demonstrates that the
optimal adversary bound for the quantum query
complexity of Boolean functions can be represented as
the solution to a semidefinite programming problem.
We aim to create a tool useful to quantum algorithm
researchers that can take in an arbitrary Boolean
function and present the optimal quantum query
complexity of the algorithm via the solution of the
corresponding semidefinite program. Our tool not only produces 
optimal quantum query complexity, but also aims to leverage 
the structure and sparsity in these problems to improve the runtime of our solver.


We store our coding implementation and work at
\url{https://github.com/rtealw/Optimal-Quantum-Algorithms}.


% the other sections
\input{sec/1_introduction.tex}
\input{sec/2_methodology.tex}
\input{sec/3_results.tex}
\input{sec/4_conclusions.tex}

% select the reference format (leave this)
\bibliographystyle{ACM-Reference-Format}

% specify the bibliography (.bib) file
% place your references in this bib file
\bibliography{main}

\end{document}